\documentclass[11pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[default]{lato}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{fontawesome}
\usepackage{enumitem}
\DeclareFontFamily{U}{fontawesomeOne}{}
\DeclareFontShape{U}{fontawesomeOne}{m}{n}
{<-> FontAwesome--fontawesomeone}{}
\DeclareRobustCommand\FAone{\fontencoding{U}\fontfamily{fontawesomeOne}\selectfont}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
{\setlength{\leftmargin}{#1}}%
     \item[]
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
{\setlength{\leftmargin}{-0.5#1}}%
\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
#1 &
#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\begin{center}
	{\LARGE \textbf{Nihan Aydın}}\\
	Software Engineer
	\vspace{0.05cm}
	\\
	\raisebox{-0.2\height} {\Large \faPhoneSquare} \ \  (544) 497-0312 \hfill\raisebox{-0.2\height}{\Large \faEnvelopeSquare} \ \ nihannuraydin@gmail.com \hfill \raisebox{-0.2\height}{\Large \faGithubSquare} \ \ github.com/nihanaydin \hfill 
\end{center}

\hrule
\vspace{-1em}
\subsection*{\Large Experience}

\renewcommand\labelitemi{}
\renewcommand\labelitemii{$\bullet$}
\begin{itemize}[leftmargin=1em]
	\parskip=0.1em
		
		
	\item
	      \headerrow
	      {\textbf{StockMount}}
	      {\textbf{Ankara, Turkey}}
	      \headerrow
	      {\emph{Software Engineering Candidate}}
	      {\emph{October 2018 – Present}}
	      \begin{itemize*}
	      	\item Created developer wikis and \textbf{technical documentation} of the entire StockMount product from scratch, ranging from Support, Developer and DevOps topics. 
	      	\item Documentation details include database maintenance, system installation and configuration, developer and testing environment setup. 
	      	\item Designed and implemented admin dashboards and interfaces to manage, create and edit operations for users.
	      \end{itemize*}
	      \headerrow
	      {\emph{Software Development Intern II}}
	      {\emph{August 2019 – September 2019}}
	      \begin{itemize*}
          \item Developed a \textbf{JSON parser} for the customers' data to generate a monthly report 
          \item Data was collected from a \textbf{MySQL} database, converted to JSON, then converted to \textbf{amChart} compatible format.
          \item Implemented queries and worked on a mock API for testing using \textbf{Mocky}
	      	
	      \end{itemize*}
	      \headerrow
	      {\emph{Software Development Intern I}}
	      {\emph{August 2018 – September 2018}}
	      \begin{itemize*}
	      	\item Received training in Google AdSense and SEO implementations for the company's web interfaces
	      	
	      \end{itemize*}
	      	      
	
	      	      
\end{itemize}

\hrule
\vspace{-1em}
\subsection*{\Large Experience}

\renewcommand\labelitemi{}
\renewcommand\labelitemii{$\bullet$}
\begin{itemize}[leftmargin=1em]
	\parskip=0.1em
		
		
	\item
	      \headerrow
	      {\textbf{ANKADES - An Educational Social Sharing Platform}}
	      {\emph{October 2018 – Present}}
	      \begin{itemize*}
	      	\item For my senior project, i have designed, implemented and documented a Learning Platform
	      	\emph complete from scratch. The project has been developed on GitHub.
	      	\item Implemented a \textbf{REST API} working as the backbone of the system, scheduling, caching and handling HTTP requests. A distribution of the project can service around 1000 concurrent requests.
	      	\item Created a management panel in \textbf{Django} for educational professionals to manage classes, participants, and inventory for written and video material, provided a straightforward interface for users.
	      \end{itemize*}
\end{itemize}

\hrule
\vspace{-1em}
\subsection*{\Large Skills}

\hyphenpenalty=1000
\begin{itemize}[leftmargin=1em,noitemsep]
	\item \textbf{Languages:}
	      C\#, HTML/CSS, JavaScript, Python, Django
	\item \textbf{Software:}
	      Atlassian (Bitbucket, Jira, Confluence), AWS (EC2, S3), Redmine, PostgreSQL
\end{itemize}

\hrule
\vspace{-1em}
\subsection*{\Large Education}

\begin{itemize}[leftmargin=1em]
	\parskip=0.1em
		
	\item
	      \headerrow
	      {\textbf{Çankaya University}}
	      {\textbf{Ankara, Turkey}}
	      \headerrow
	      {\emph{B.Sc. Computer Engineering}}
	      {\emph{September 2015 -- June 2021}}
	      	      
\end{itemize}

\end{document}